---
author: Vibeesh Kamalakannan
date: 2022-10-28
generator: pandoc
title: Best Trials
viewport: width=device-width, initial-scale=1
---

``` {r options(warn = -1)}
library(tidyverse)
library(dplyr)
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(ggplot2)
library(hrbrthemes)
```

``` {r}
data = read.csv('national_park_trails.csv')
```

**In this project, we are tasked to work like an analyst to find out
which features or activities are a part of the best trails in the USA. I
decided that the popularity and average rating were the main factors
that determined how good the trails are. I made a ranked list of most
frequently occurring features and activities occurring only in the top 90
percentile of popularity and average rating. But before that, I did some
analysis to check if there were other variables that had an effect on
the popularity.**

``` {r}
summary(data$popularity)
```

``` {r}
summary(data$avg_rating)
```

``` {r options(warn = -1)}
ggplot(data=data, aes(x=popularity, y=elevation_gain))+
  geom_point() + theme_ft_rc() 
```

``` {r}
ggplot(data=data, aes(x=popularity, y=length))+
  geom_point() + theme_ft_rc()
```
**I made the above two visualizations to check if there is a correlation
between elevation gain or length with the popularity. We cannot confirm
that there is a correlation. But we can say that the popularity for most
trails are between 0-40.**

``` {r}
ggplot(data=data, aes(x=factor(difficulty_rating), y= popularity )) +
  geom_bar(stat="identity") + theme_ft_rc() + xlab('Difficulty Rating')
```
**From the above graph, we can see that trails with a difficulty rating
of 3 is the most popular. and drops off as the rating increases. People
also don't seem to like trails that are too easy (difficulty rating
1).**

``` {r}
ggplot(data=data, aes(x=route_type, y= popularity )) +
  geom_bar(stat="identity") + theme_ft_rc()
```

``` {r}
ggplot(data=drop_na(data), aes(x=factor(visitor_usage), y= popularity )) +
  geom_bar(stat="identity") + theme_ft_rc()  + xlab('Visitor Usage')
```

``` {r}
ggplot(data=data, aes(x=popularity, y=factor(avg_rating)))+
  geom_bar(stat="identity") + theme_ft_rc() +   ylab('Average Rating')
```

**I assumed that the more popular trails would have a higher average
rating. This proved to be true as seen in the graph above. trails with a
popularity score of 5000 and above have the highest ratings.**

## Most popular states

**Below, we see the states with the highest average popularity scores.**
``` {r}
data %>% 
  group_by(state_name) %>% 
  summarise(Mean_popularity = mean(popularity)) %>%
  arrange(desc(Mean_popularity))
```
## Most popular areas

**The areas with the highest average popularity scores are shown
below.**
``` {r}
data %>% 
  group_by(area_name) %>% 
  summarise(Mean_popularity = mean(popularity)) %>%
  arrange(desc(Mean_popularity))
```
## Function to find out frequency of occurences of words.

**I wrote a function to find out the frequency of occurrences words in a
list. With this function we can find out which words occur the most
frequently in the activities and features column. This function first
performs data cleaning before extracting the frequency of words.**

``` {r}
frequency = function (cols){
      a = gsub("\\[|\\]", "", cols)
      
      a = gsub("'", "", a)
      
      b = c()
      
      for (i in a){
        b=c(b, as.list(el(strsplit(i, ","))))
      }
      
      
      y = paste(b, collapse = " ")
      
      freq = sort(table(unlist(strsplit(y, " ") ) ),     
                     decreasing = TRUE)
      df = as.data.frame(freq)[-1,]
      
      colnames(df)[1] <- 'Word'
      
      return (df)
}
```
## Function to create a word cloud.

**The function below is used to create a word cloud for the most
frequently occuring words. This is done using the libraries "tm",
"SnowballC". "wordcloud" and "RColorBrewer".**

``` {r}
word_cloud = function(col) {
a = gsub("\\[|\\]", "", col)

a = gsub("'", "", a)

b = c()

for (i in a){
  b=c(b, as.list(el(strsplit(i, ","))))
}


y = paste(b, collapse = " ")

Corpus(VectorSource(y))   

docs <- Corpus(VectorSource(y))
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")
# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove your own stop word
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
# Text stemming
# docs <- tm_map(docs, stemDocument)
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

return (wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2")) )
}
```
## Word cloud for features for all trails.

``` {r}
word_cloud(data$features)
```
## Word cloud for activities for all trails.

::: {#cb27 .sourceCode}
``` {r}
word_cloud(data$activities)
```
## Frequency of features in all trails

``` {r}
frequency(data$features)
```

## Frequency of activities in all trails.

``` {r}
frequency(data$activities)
```

## Filtering for top 90 percentile of popularity score and average rating.
``` {r}
a = quantile(data$popularity, probs = 0.9)
b = quantile(data$avg_rating, probs = 0.9)   
top_data = data %>%
  filter(avg_rating >=b & popularity>=a)
summary(top_data)
```

## Frequency of activities for the best trails in the USA.

**Below, we can see the most commonly occuring activities for the best
trails in the US. I performed this with the frequency function created
earlier.**

``` {r}
frequency(top_data$activities)
```
## Frequency of features for the best trails in the USA.

**The features that are a part of of the best trails in the US are shown
below.**

``` {r}
frequency(top_data$features)
```
## Wordcloud for most common activities

**The frequency of activities of the best trails are displayed as a word
cloud below.**

``` {r}
word_cloud(top_data$activities)
```
## Wordcloud for most common features

**The frequency of features of the best trails are displayed as a word
cloud below.**

``` {r}
word_cloud(top_data$features)
```

**As mentioned before, I decided that the best trails are the ones above
the 95th percentile of popularity score and average rating. We get 89
such trails. In these trails, from the word cloud and the frequency
tables we notice that views, dogs-no, wildlife and wildflowers are the
most frequently occurring features. And when we consider activities,
hiking, nature-trips and birding are the most frequently occurring
activities for the best trails in the USA.**
